---
date: 2024-02-07
title: 'Daily Update – Feb 07, 2024'
format: 
    html:
      toc: false
title-block-banner: true
execute:
    echo: false
    warning: false
    message: false
---
'Africans Are The Only People Who Demonize Their Own Traditional Religions. Here’s Why.; South African Woman Couldn&#39;t Believe She Was Asked If Lions Were In Her Village; Facebook&#39;s Strategic Shift to the Metaverse; On 1865, the 13th Amendment of the United States Constitution was passed, abolishing slavery.; Pan-African Attitude Ep.1 - Kenya High Court Ruling On Haiti'

```{r}

library(tidyverse)

videos_tbl <- read_csv('videos_tbl.csv') |> 
  mutate(embeds = embeds |> 
           str_replace_all('480', '100%') |> 
           str_replace_all('270', '50%'))

```

```{r}
#| echo: false

# A list of summaries:

 
videos_joined <- videos_tbl |> 
    select(publishedAt,title, description, embeds, 
           channelId, category) |> 
    filter(publishedAt >= lubridate::ymd('2024-02-07')-1)

videos <- videos_joined |>  
    split(videos_joined$category) 
    

headings <- names(videos)
#videos
```

## Today's Videos

::: panel-tabset
```{r, results='asis'}
#| warning: false


for (i in seq_along(videos)) {
    cat("# ",headings[i],"\n")
    current_df <- videos[[i]]
  
    
    for (j in seq_along(current_df$embeds)) {
        current_value <- current_df$embeds[j]
        
        current_title <- current_df$title[j]
        cat("### ",current_title,"\n")
        cat(current_value)
        cat("\n")
        cat("\n") 
         
         
         
 }
}
```
:::
